### 2019-10-21 2018_nips_vigil/conclusion.tex

\section{Conclusion}
We have introduced SMAC, a simplified version on the MAC model. Our version proposes simplified equations and therefore we could reduce significantly the number of parameters in the MAC cell, which is the recurrent unit of the model. As a result we could decrease training time by more than two hours ( reduction by almost 10 \%)
while maintaining an equivalent test accuracy. 
We have also evaluated generalization capabilities of MAC and S-MAC on the CLEVR CoGenT dataset.
The results of our experiments first show that MAC and SMAC perform equally well on all the CoGenT task. Thus the simplifications did not alter SMAC generalization capability.
Furthermore, MAC and SMAC compare favorably with state-of-the-art models on the CoGenT taks. MAC and SMAC present competitive generalization and transfer learning capacities.
Nevertheless, CLEVR CoGenT remains an unsolved problem. The MAC model still struggles to learn distinct concepts. We could see that MAC sometimes fail to differentiate colors and shape as two distinct features of the same object.

>>>>

\section{Conclusion}
We have introduced S-MAC, a simplified variant of the MAC model. Because it has nearly half the number of parameters in the recurrent portion MAC cell, it trains faster while maintaining an equivalent test accuracy.

Our experiments on zero-short learning show that the MAC model has poor performance in line with the other models in the literature. Thus, this remains an interesting problem to investigate how we can train it to disentangle the concepts of shape and color.

With fine-tuning, the MAC model indeed achieves much improved performance, matching state of the art. However, we have showed that correlation between the different domains must be taken into account when fine-tuning, otherwise potentially leading to decreased performance.

### 2019-10-21 arxiv/experiments.tex
polishing

Our experiments were intended to study MAC's and S-MAC's generalization as well as transfer learning abilities in different settings. We used CLEVR and CoGenT to address these different aspects.
The first experiment studied the training time and the capability of the models to generalize on the same type of dataset that it was trained on. This was used mainly as a baseline for the further experiments that were intended to study how well the transfer learning performed in comparison to the baseline results.
The second experiment studied the capability of the models to succeed in doing transfer learning from domain A to domain B when trained on different combinations of the respective domains. The third experiment was intended to see whether the performance improves if the model could be further trained on a small subset of the dataset from domain B.
\tableref{results} presents the most important results, focusing on S-MAC in particular; see Appendix~\ref{sec:full_comparison} for the entire set.

@@

		\bottomrule
	\end{tabular}
	\label{results}
\end{table}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{../img/fail_mac_cogent_b_shape.png}
	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
	\label{fig:fail_mac_shape}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{../img/fail_mac_cogent_b_color.png}
	\caption{The question reads as: \textit{There is a tiny block behind the rubber thing that is right if the small brown rubber cylinder that is in front of the yellow metal cylinder; what color is it?}}
	\label{fig:fail_mac_color}
\end{figure}

>>>>

Our experiments were intended to study MAC's and S-MAC's generalization as well as transfer learning abilities in different settings. We used CLEVR and CoGenT to address these different aspects.
The first experiment studied the training time and the capability of the models to generalize on the same type of dataset that it was trained on. This was used mainly as a baseline for the further experiments that were intended to study how well the transfer learning performed in comparison to the baseline results.
The second experiment studied the capability of the models to succeed in doing transfer learning from domain A to domain B when trained on different combinations of the respective domains. The third experiment was intended to see whether the performance improves if the model could be further trained on a small subset of the dataset from domain B.
\tableref{tab:results} presents the most important results, focusing on S-MAC in particular; see Appendix~\ref{sec:full_comparison} for the entire set.

@@

		\bottomrule
	\end{tabular}
	\label{tab:results}
\end{table}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{\dir/img/fail_mac_cogent_b_shape.png}
	\caption{The question reads as: \textit{There is a large gray thing that is on the right side of the big gray cylinder left of the large ball that is on the right side if the cyan rubber sphere; what is its shape?}}
	\label{fig:fail_mac_shape}
\end{figure}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\textwidth]{\dir/img/fail_mac_cogent_b_color.png}
	\caption{The question reads as: \textit{There is a tiny block behind the rubber thing that is right if the small brown rubber cylinder that is in front of the yellow metal cylinder; what color is it?}}
	\label{fig:fail_mac_color}
\end{figure}
